Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-10-10 paper/paper.Rmd
catch another missing comma

knitr::kable(observations
  caption = "(\\#tab:observations) Observations on the relative performance of the Forecast Hub ensemble compared to our forecast submissions." # nolint
)
```

>>>>

knitr::kable(observations,
  caption = "(\\#tab:observations) Observations on the relative performance of the Forecast Hub ensemble compared to our forecast submissions." # nolint
)
```
